CSD, Disjoint components and trayectory detection

### 2019-04-29 ArticuloCSDyCM/Paper03.tex
figuras tres columnas salieron ya

@@

>>>>

The figure \ref{lfpcsdcm}  compares the representation of the activity in
the LFP, CSD and CM spaces. It has been exhaustively proven that the CSD
representation provides better spatial localization of active sites, but the
CM can serve as better dinamical tracker of action. The figure ilustrates
that point by choosing the time interval of response in CA3 after the stimulus.
CM representation permits us to track the activity with less
interference from the saturated region. The small, clearly localized centers of
mass separate clearly from the big patch over the saturated region.
In the figure \ref{evotracks} we concatenate the succesive centers of mass
for both sinks and sources and show how the anterograde reaction is
very well localized over the Pyramidal Stratum at precise moments after
stimulus.

@@

\begin{figure}[h]
  \includegraphics[width=0.9\textwidth]{Figuras/CSD_Evocada01.pdf}
  \caption{ A comparision of the representations of the displacement of the
    activity. We show several timeframes after stimulus in three representations.
    the leftmost column shows the averaged LFP as measured by the BioCAM.
    In the center column we have the CSD representation, as obtained by
    the kCSD method. In the right column we superimpose over the CSD representation
    the Centers of Mass of each disconnected component, for both sinks and
    sources. In the three columns the saturation of electrodes near
    the point of stimulus is quite evident. Nevertheless, the CSD representation
    provides much better contrast and the patches are better localized as espected.
    The Centers of Mass provide a clear locus of the active subsets of units.
    The area of the circular dots represent the integrated density. The
    bigger ones at the right edge cover the saturated electrodes.
    The anterograde movement of activity follows a high ``sink center'' in the
    first three rows, and then it is followed by a ``source center'', of aproximately
    the same integrated ``mass'', that ends spliting in three smaller components.    
  }\label{lfpcsdcm}
\end{figure}
